---
title: "autoQC report"
author: "SIgN_GM"
output: html_document
---


```{r setup, include=FALSE}
#knitr::opts_chunk$set(cache=FALSE)
opts_chunk$set(fig.align='center', out.width='750px', dpi=200)  #out.width='750px', dpi=200
#opts_chunk$set(dev = 'pdf')
```

## AutoQuality Control Report

> Input File Name: `r filename`    
> Number of Cells: `r as.integer(dim(set[[i]])[1])`  
> The anomalies were removed from:  `r analysis`   
> Anomalies Detected in total: **`r totalBadPerc * 100`** %  


### Number of cells in each FCS file:

If the number of FCS files is higher than 3, a histogram reports the number of
cells for each FCS file of the dataset. In blue is highlighted the FCS file 
whose quality control analysis is described in this report.


```{r, echo=FALSE, fig.height = 3}
if(length(set) >= 3 ){
  flow_set_plot(N_cell_set, area)
}
```


### Flow Rate Check

> **`r FlowRateQC$res_fr_QC$badPerc * 100`** % Anomalies Detected in the Flow Rate Check.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 4, fig.width= 10}
  if (length(nchar(timeCh)) != 0 && !is.null(timeCh)) {   
        flow_rate_plot(FlowRateQC) 
} 
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
  if (length(nchar(timeCh)) == 0 || is.null(timeCh)) {   
        cat("It was not possible to analyse the flow rate since the \"Time\" channel was missing. \n")
   }
```

The plot reconstructs the flow rate with a resolution of 1/`r 1/second_fractionFR` of a second. Anomalies in the flow rate have been detected with an algorithm based on the ESD outlier detection method. The anomalies automatically detected are circled in green.

### Signals' Channel Check

> **`r FlowSignalQC$Perc_bad_cells$badPerc_tot * 100`** % Anomalies Detected in the Flow Signal Check. 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
  if (outlierFS) { 
        cat(paste0("Outliers were removed before the changepoint analysis.", FlowSignalQC$Perc_bad_cells$badPerc_out * 100, "% of anomalies were detected as outliers and ", FlowSignalQC$Perc_bad_cells$badPerc_cp *100, " of anomalies were detected in the changepoint analysis. \n"))
   }
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height = h_FS_graph}
flow_signal_plot(FlowSignalQC)
```

The more stable region selected consistent for all channels is highlighted in yellow. If the outlier removal has been required before the changepoint analysis, then the detected outliers are cicled in green.

The FCS file was divided in `r FlowSignalData$bins` segments. The stable region is located between the segment `r FlowSignalQC$segm[1]` and `r FlowSignalQC$segm[2]`.

##### More info on the changepoints detected:

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
if(!is.null(FlowSignalQC$tab_cpt)){
     cat("Channels where shifts in signal intensities were detected with corresping changepoints:  \n")
}else{
  cat("No changepoints were detected.  \n")
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 10, fig.height = 4}
if(!is.null(FlowSignalQC$tab_cpt)){
   as.data.frame(FlowSignalQC$tab_cpt )
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
if(!is.null(ChRemoveFS)){
     cat(paste0("Channels excluded from the analysis: ", paste(ChannelRemovedFS, collapse = ", "), ". \n"))
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 10, fig.height = 4, results = 'asis'}
if(!is.null(FlowSignalQC$ch_no_cpt) && length(FlowSignalQC$ch_no_cpt) != 0 ){
  cat(paste0("Channels where no changepoints were detected: ", paste(FlowSignalQC$ch_no_cpt, collapse = ", "), ". \n"))
}
```

### Margin Events Check

> **`r FlowMarginQC$badPerc * 100`** % Anomalies Detected in Margin Events Check.  

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 4, fig.width= 10}
flow_margin_plot(FlowMarginQC, FSbinSize)
```

The plot shows where the margin events occur mostly. The x-axis scale is complementary to the one of the Flow Signal plot.

##### More info on the margin events detected:

```{r, echo=FALSE, warning=FALSE, message=FALSE}
FlowMarginQC$margin_events
```

The table shows the number of cells that did not pass the check for each channel.

